---
title: "COVID-19 Content Promoted by reddit"
output:
    rmdformats::readthedown:
    html_document:
        toc: true
        theme: readthedown
        code_folding: hide
date: '`r format(Sys.Date(), "%B %d, %Y")`'
author: 
    - J. Nathan Matias [Cornell University](https://citizensandtech.org)
    - Eric Pennington [Citizens and Technology Lab](https://citizensandtech.org)
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE)
```


````{r results=FALSE, echo=FALSE}
## load libraries
library(ggplot2)
library(DescTools)

## Set visual style
catpalette   <- c("#333333", "#ea5324", "#005073", "#7D868C", "#BDBBBB", "#F2F2F2","#F6F2EB")
covidpalette   <- c("#666666", "#ea5324", "#005073", "#7D868C", "#BDBBBB", "#F2F2F2","#F6F2EB")

chartpalette <- c("#ea5324", "#005073", "#7D868C", "#333333", "#F2F2F2","#BDBBBB", "#F6F2EB")

cat.theme <-  theme_bw() +
              theme(plot.title = element_text(size=13, face="bold", color=catpalette[3]),
                    axis.title.x =element_text(size=10, hjust = -0.01, color = catpalette[1]),
                    axis.title.y =element_text(size=10, color = catpalette[1]),
                    panel.background = element_rect(fill=catpalette[6]))
options(repr.plot.width=6, repr.plot.height=3)

## set directories
HOME.DIR = "/home/nathan/covid-algotracker"
most.recent.folder.name <- as.character(max(as.numeric(SplitPath(Sys.glob(
        file.path(HOME.DIR, "data-archive", "reddit", "[0-9]*")))$filename)))
DATA.FOLDER = file.path(HOME.DIR, "data-archive", "reddit", most.recent.folder.name)
Sys.glob(file.path(DATA.FOLDER, "*"))

######################
## Utility Methods
cat.post <- function(post, ranking){
    cat(paste("<li> (", post['rank_position'], ") (",post['num_comments.x'],"💬) <strong><a href='https://np.reddit.com", 
              post['permalink'], "'>", post['title'], "</a></strong>",
              "<ul><li><small><strong>r/",post['subreddit'], 
              "</strong>. Domain: ",post['domain'],
              ". Highest Rank: ", 
              post[paste("max_", ranking, sep="")], ". ",
              "Time on ", ranking, ": ", 
              as.integer(as.numeric(post[paste("front_", ranking, "_seconds", sep="")])/60.),
              " minutes</small></li></ul></small></li>", sep=""))
}

##############################
## load posts and rankings
hot.ranks <- read.csv(file.path(DATA.FOLDER, 
                               paste("rank_timeseries_hot_",
                                     most.recent.folder.name,
                                     ".csv", sep="")))
hot.ranks$snapshot.num <- sequence(rle(as.character(hot.ranks$id))$lengths)


top.ranks <- read.csv(file.path(DATA.FOLDER, 
                               paste("rank_timeseries_top_",
                                     most.recent.folder.name,
                                     ".csv", sep="")))
top.ranks$snapshot.num <- sequence(rle(as.character(top.ranks$id))$lengths)



recent.posts  <- read.csv(file.path(DATA.FOLDER, 
                               paste("promoted_posts_",
                                     most.recent.folder.name,
                                     ".csv", sep="")))

#####################################
## Create ranking and post subsets
latest.hot.ranking <- max(hot.ranks$rank_id)
latest.top.ranking <- max(top.ranks$rank_id)

latest.hot.ranks <- subset(hot.ranks, rank_id == latest.hot.ranking & is.na(ups)!=TRUE)
latest.hot.rank.ids <- unique(latest.hot.ranks$id)
latest.top.ranks <- subset(top.ranks, rank_id == latest.top.ranking & is.na(ups)!=TRUE)
latest.top.rank.ids <- unique(latest.top.ranks$id)

latest.hot.posts <- merge(subset(recent.posts, in_latest_snapshot_hot == 1), latest.hot.ranks, by=c("id"))
latest.top.posts <- merge(subset(recent.posts, in_latest_snapshot_top == 1), latest.top.ranks, by=c("id"))

latest.hot.posts <- latest.hot.posts[order(-latest.hot.posts$rank_position),]
latest.top.posts <- latest.top.posts[order(-latest.top.posts$rank_position),]

latest.hot.rank.snapshots <- subset(hot.ranks, id %in% latest.hot.rank.ids)
latest.hot.rank.snapshots$rank.time <- as.POSIXct(latest.hot.rank.snapshots$rank_time, origin="1970-01-01")
latest.hot.rank.snapshots$age.minutes <- as.integer((latest.hot.rank.snapshots$rank.time - max(latest.hot.rank.snapshots$rank.time))/60)

latest.top.rank.snapshots <- subset(top.ranks, id %in% latest.top.rank.ids)
latest.top.rank.snapshots$rank.time <- as.POSIXct(latest.top.rank.snapshots$rank_time, origin="1970-01-01")
latest.top.rank.snapshots$age.minutes <- as.integer((latest.top.rank.snapshots$rank.time - max(latest.top.rank.snapshots$rank.time))/60)
````

*Latest HOT Snapshot taken: `r as.POSIXct(unique(latest.hot.ranks$rank_time))`. Latest TOP Snapshot taken: `r as.POSIXct(unique(latest.top.ranks$rank_time))`*

TODO: a description of the page goes here.

# Currently-Promoted COVID-19 Posts on Reddit

## Posts Currently Promoted by the HOT Algorithm

<ul>
````{r echo = FALSE, results='asis'}
apply(subset(latest.hot.posts, covid_19.x==1), 1, FUN=cat.post, ranking="hot")
````
</ul>

## Posts Currently Promoted by the TOP Algorithm

<ul>
````{r echo = FALSE, results='asis'}
apply(subset(latest.top.posts, covid_19.x==1), 1, FUN=cat.post, ranking="top")
````
</ul>

## Reddit's HOT Ranking

List of posts

````{r echo = FALSE, results=FALSE, fig.width=10, fig.height=3}

ggplot(latest.hot.rank.snapshots, aes(age.minutes, rank_position, group=id, col=factor(covid_19))) +
    geom_line() + 
    cat.theme +
    scale_colour_manual(values = covidpalette, name="COVID-19\nrelated") +
    xlim(-480, 0) +
    ylab("Rank position")  +
    xlab("Minutes prior to the snapshot (up to 8 hours)") +
    ggtitle("Rank Position of COVID-19 Posts currently the front page of reddit (HOT)")
````

## Reddit's TOP Ranking

````{r echo=FALSE, results=FALSE, fig.width=10, fig.height=3}
ggplot(latest.top.rank.snapshots, aes(age.minutes, rank_position, group=id, col=factor(covid_19))) +
    geom_line() + 
    cat.theme +
    scale_colour_manual(values = covidpalette, name="COVID-19\nrelated") +
    xlim(-900, 0) +
    ylab("Rank position")  +
    xlab("Minutes prior to the snapshot (up to 15 hours)") +
    ggtitle("Rank Position of COVID-19 Posts currently the front page of reddit (TOP)")
````

# Top Promoted Subreddits

# Top Promoted Sources
