---
title: "COVID-19 Content Promoted by reddit"
output:
    rmdformats::readthedown:
    html_document:
        toc: true
        theme: readthedown
        code_folding: hide
date: '`r format(Sys.Date(), "%B %d, %Y")`'
author: 
    - name: J. Nathan Matias
      affiliation: "<a href='https://citizensandtech.org'>CAT Lab, Cornell University</a>"
    - name: Eric Pennington 
      affiliation: "<a href='https://citizensandtech.org'>CAT Lab, Cornell University</a>"
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE)
```


````{r results=FALSE, echo=FALSE}
## load libraries
library(ggplot2)
library(DescTools)
library(knitr)

## Set visual style
catpalette   <- c("#333333", "#ea5324", "#005073", "#7D868C", "#BDBBBB", "#F2F2F2","#F6F2EB")
covidpalette   <- c("#666666", "#ea5324", "#005073", "#7D868C", "#BDBBBB", "#F2F2F2","#F6F2EB")

chartpalette <- c("#ea5324", "#005073", "#7D868C", "#333333", "#F2F2F2","#BDBBBB", "#F6F2EB")

cat.theme <-  theme_bw() +
              theme(plot.title = element_text(size=13, face="bold", color=catpalette[3]),
                    axis.title.x =element_text(size=10, hjust = -0.01, color = catpalette[1]),
                    axis.title.y =element_text(size=10, color = catpalette[1]),
                    panel.background = element_rect(fill=catpalette[6]))
options(repr.plot.width=6, repr.plot.height=3)

## set directories
HOME.DIR = "/home/nathan/covid-algotracker"
most.recent.folder.name <- as.character(max(as.numeric(SplitPath(Sys.glob(
        file.path(HOME.DIR, "data-archive", "reddit", "[0-9]*")))$filename)))
DATA.FOLDER = file.path(HOME.DIR, "data-archive", "reddit", most.recent.folder.name)
Sys.glob(file.path(DATA.FOLDER, "*"))

######################
## Utility Methods
cat.post <- function(post, ranking){
    cat(paste("<li> <small>(", post['rank_position'], ")",
              "(🔺",post['ups'], ")",
              "</small> <strong><a href='https://np.reddit.com", 
              post['permalink'], "'>", post['title'], "</a></strong>",
              "<ul><li><small><strong>r/",post['subreddit'], 
              "</strong>. ",
              "(💬",post['num_comments.x'], ") ",
              "Domain: ",post['domain'], ". ",
              "Highest Rank: ", 
              post[paste("max_", ranking, sep="")], ". ",
              "Time on ", ranking, ": ", 
              as.integer(as.numeric(post[paste("front_", ranking, "_seconds", sep="")])/60.),
              " minutes</small></li></ul></small></li>", sep=""))
}

##############################
## load posts and rankings
hot.ranks <- read.csv(file.path(DATA.FOLDER, 
                               paste("rank_timeseries_hot_",
                                     most.recent.folder.name,
                                     ".csv", sep="")))
hot.ranks$snapshot.num <- sequence(rle(as.character(hot.ranks$id))$lengths)


top.ranks <- read.csv(file.path(DATA.FOLDER, 
                               paste("rank_timeseries_top_",
                                     most.recent.folder.name,
                                     ".csv", sep="")))
top.ranks$snapshot.num <- sequence(rle(as.character(top.ranks$id))$lengths)



recent.posts  <- read.csv(file.path(DATA.FOLDER, 
                               paste("promoted_posts_",
                                     most.recent.folder.name,
                                     ".csv", sep="")))

observation.period.days <- as.integer(round(max(as.POSIXct(top.ranks$rank_time)) - min(as.POSIXct(top.ranks$rank_time))))

#####################################
## Create ranking and post subsets
latest.hot.ranking <- max(hot.ranks$rank_id)
latest.top.ranking <- max(top.ranks$rank_id)

latest.hot.ranks <- subset(hot.ranks, rank_id == latest.hot.ranking & is.na(ups)!=TRUE)
latest.hot.rank.ids <- unique(latest.hot.ranks$id)
latest.top.ranks <- subset(top.ranks, rank_id == latest.top.ranking & is.na(ups)!=TRUE)
latest.top.rank.ids <- unique(latest.top.ranks$id)

latest.hot.posts <- merge(subset(recent.posts, in_latest_snapshot_hot == 1), latest.hot.ranks, by=c("id"))
latest.top.posts <- merge(subset(recent.posts, in_latest_snapshot_top == 1), latest.top.ranks, by=c("id"))

latest.hot.posts <- latest.hot.posts[order(-latest.hot.posts$rank_position),]
latest.top.posts <- latest.top.posts[order(-latest.top.posts$rank_position),]

latest.hot.rank.snapshots <- subset(hot.ranks, id %in% latest.hot.rank.ids)
latest.hot.rank.snapshots$rank.time <- as.POSIXct(latest.hot.rank.snapshots$rank_time, origin="1970-01-01")
latest.hot.rank.snapshots$age.minutes <- as.integer((latest.hot.rank.snapshots$rank.time - max(latest.hot.rank.snapshots$rank.time))/60)

latest.top.rank.snapshots <- subset(top.ranks, id %in% latest.top.rank.ids)
latest.top.rank.snapshots$rank.time <- as.POSIXct(latest.top.rank.snapshots$rank_time, origin="1970-01-01")
latest.top.rank.snapshots$age.minutes <- as.integer((latest.top.rank.snapshots$rank.time - max(latest.top.rank.snapshots$rank.time))/60)
````

<!-- Matomo -->
<script type="text/javascript">
  if (window.location.hostname == "covid-algotracker.citizensandtech.org") {
    var _paq = window._paq || [];
    /* tracker methods like "setCustomDimension" should be called before "trackPageView" */
    _paq.push(['trackPageView']);
    _paq.push(['enableLinkTracking']);
    (function() {
      var u="https://citizensandtech.matomo.cloud/";
      _paq.push(['setTrackerUrl', u+'matomo.php']);
      _paq.push(['setSiteId', '1']);
      var d=document, g=d.createElement('script'), s=d.getElementsByTagName('script')[0];
      g.type='text/javascript'; g.async=true; g.defer=true; g.src='//cdn.matomo.cloud/citizensandtech.matomo.cloud/matomo.js'; s.parentNode.insertBefore(g,s);
    })();
  }
</script>
<!-- End Matomo Code -->


*Latest HOT Snapshot taken: `r as.POSIXct(unique(latest.hot.ranks$rank_time))`. Latest TOP Snapshot taken: `r as.POSIXct(unique(latest.top.ranks$rank_time))`*

TODO: a description of the page goes here.

## How We Collect Data

## How We Identify COVID-19 Posts

# Currently-Promoted COVID-19 Posts on Reddit

## Posts Currently Promoted by the HOT Algorithm

In the latest snapshot, `r sprintf("%.01f", (sum(latest.hot.posts$covid_19.x) / nrow(latest.hot.posts))*100)`% of posts appearing in the HOT algorithm on reddit are COVID-19 related.

<ul>
````{r echo = FALSE, results='asis'}
apply(subset(latest.hot.posts, covid_19.x==1), 1, FUN=cat.post, ranking="hot")
````
</ul>

````{r echo = FALSE, results=FALSE, fig.width=10, fig.height=3}

min.hot.xlim = floor(min(subset(latest.hot.rank.snapshots, is.na(rank_position)!=T)$age.minutes)/60)*60

ggplot(latest.hot.rank.snapshots, aes(age.minutes, rank_position, group=id, col=factor(covid_19))) +
    geom_line() + 
    cat.theme +
    scale_colour_manual(values = covidpalette, name="COVID-19\nrelated") +
    scale_x_continuous(breaks=seq(min.hot.xlim, 0, 60), limits=c(min.hot.xlim, 0)) + 
    ylab("Rank position")  +
    ggtitle("Rank Position of COVID-19 Posts currently the front page of reddit (HOT)") +
    xlab(paste("Minutes prior to the snapshot (up to ",abs(min.hot.xlim/60), " hours)", sep=""))

````

## Posts Currently Promoted by the TOP Algorithm


In the latest snapshot, `r sprintf("%.01f", (sum(latest.top.posts$covid_19.x) / nrow(latest.top.posts))*100)`% of posts appearing in the TOP algorithm on reddit are COVID-19 related.

<ul>
````{r echo = FALSE, results='asis'}
apply(subset(latest.top.posts, covid_19.x==1), 1, FUN=cat.post, ranking="top")
````
</ul>


````{r echo=FALSE, results=FALSE, fig.width=10, fig.height=3}
min.top.xlim = floor(min(subset(latest.top.rank.snapshots, is.na(rank_position)!=T)$age.minutes)/60)*60

ggplot(latest.top.rank.snapshots, aes(age.minutes, rank_position, group=id, col=factor(covid_19))) +
    geom_line() + 
    cat.theme +
    scale_colour_manual(values = covidpalette, name="COVID-19\nrelated") +
    scale_x_continuous(breaks=seq(min.top.xlim, 0, 60), limits=c(min.top.xlim, 0)) + 
    ylab("Rank position")  +
    ggtitle("Rank Position of COVID-19 Posts currently the front page of reddit (TOP)") +
    xlab(paste("Minutes prior to the snapshot (up to ",abs(min.top.xlim/60), " hours)", sep=""))
````

# Communities and Sources

## Communities and Sources Promoted by Reddit's HOT Algorithm

```{r echo=FALSE, results=TRUE}
num.top.obs = 15

recent.subs <- as.data.frame(table(as.character(subset(recent.posts, covid_19==1)$subreddit)))
recommended.subs <- head(recent.subs[order(-recent.subs$Freq),], num.top.obs)
row.names(recommended.subs) <- recommended.subs$Var1
names(recommended.subs) <- c("subreddit", "frequency")
kable(recommended.subs[c("frequency")],
    caption=paste("Top ", num.top.obs, " subreddits with COVID-19 content promoted by reddit's algorithms in the past ",
                  observation.period.days, " days.",sep=""))

````


```{r echo=FALSE, results=TRUE}
recent.domains <- as.data.frame(table(as.character(subset(recent.posts, covid_19==1)$domain)))
recommended.domains <- head(recent.domains[order(-recent.domains$Freq),], num.top.obs)
row.names(recommended.domains) <- recommended.domains$Var1
names(recommended.domains) <- c("domain", "frequency")
kable(recommended.domains[c("frequency")],
    caption=paste("Top ",num.top.obs," web domains with COVID-19 content promoted by reddit's algorithms in the past ",
                  observation.period.days, " days.",sep=""))

````
